NFC and burnout in teachers - A replication and extension study

### 2021-09-09 Manuscript/Manuscript.Rmd
updated mediation model and plot

  # It looked like there was an outlier in the data, especially visible in the MBI data
  # Check for the outlier in particular

  # Remove the outlier
  score_data <- score_data[score_data$mbi < 100, ]

@@

  repli_model <- '
  # direct paths
    scs ~ a1 * ncs
    erq_reap ~ a2 * ncs
    erq_supp ~ a3 * ncs
    mbi_rpe ~ b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs

@@

  fit_plot <- semPaths(fit, what="par", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,0.5,0,-0.5,0,0), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
                       edge.label.cex = 1, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
)
```

>>>>

  # It looked like there was an outlier in the data, especially visible in the MBI data
  # Check for the outlier in particular, using the data involved in the mediation
  outlierplot <- outlier(score_data[ ,c(6,8:11)], plot = TRUE)

  # Remove participant 161
  score_data <- score_data[score_data$mbi < 100, ]

@@

  repli_model <- '
  # direct paths
    scs       ~   a1 * ncs + years
    erq_reap  ~   a2 * ncs
    erq_supp  ~   a3 * ncs
    mbi_rpe   ~   b1 * scs + b2 * erq_reap + b3 * erq_supp + c * ncs

@@

  fit_plot <- semPaths(fit, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
                       layout = matrix(data = c(0,0,0,1,-1,-1,0.5,-0.1,-0.4,0.2,0.2,0.5), nrow = 6, ncol = 2), # manually set the node locations
                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
                       edge.label.cex = 1, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       exoCov = FALSE, # do not plot covariance between exogenous variables
                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
)
```
